### 2014-02-23 paper/retrofit.tex
Mini-note, remove when we fix the text or the rules
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

We consider languages in the form of abstract state machines |(tS, tE,
te, ->)|, where |tS| is the global machine state, |tE| is an evaluation
context, |te| is an expression in the language and |->| is the
reduction relation on such configuration, i.e., $|->| : (|tS| \times
|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$

>>>>

We consider languages in the form of abstract state machines |(tS, tE,
te, ->)|, where |tS| is the global machine state, |tE| is an evaluation
context, |te| is an expression in the language and |->| is the
reduction relation on such configuration, i.e., $|->| : (|tS| \times
|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$ \Red{This doesn't match the way the evaluation rules are currently done with a frame rule}
